A Machine Profile Summary

### 2021-12-18 MachineSummary/MachineSummary.Rmd
tidy authorship

---
title: "A Machine Profile Summary"
author: 
  - John C. Nash, University of Ottawa, Canada
date: "14/06/2021"
bibliography: ../BibSupport/ImproveNLS.bib
output: 
  pdf_document:
    keep_tex: false
---

>>>>

---
title: "A Machine Profile Summary"
author: 
   - John C. Nash \thanks{ retired professor, Telfer School of Management, University of Ottawa}
   - Arkajyoti Bhattacharjee \thanks{Department of Mathematics and Statistics, Indian Institute of Technology, Kanpur}
date: "14/06/2021"
bibliography: ../BibSupport/ImproveNLS.bib
output: 
  pdf_document:
    keep_tex: false
---
